---
title: "Quiz 1: Data Visualization"
author: "Baron Poisson"
output: html_document
---

As soon as you open this document, you should knit it to make sure it knits.

```{r message=FALSE}
library(tidyverse)
library(openintro)
library(ggplot2)
options(scipen=10000)
metro_bike <- read_csv("data/metro-bike.csv")
```

The following questions will be based on the bike rental data in Los Angeles. The data represents all bike rides from Metro Bike Share company in April-June of 2019. 

The data and a description of each variable can be found at (https://bikeshare.metro.net/about/data/).

Throughout the homework, make sure you use a reasonable font size and label axes. You are welcome to use colors and themes whenever you would like. Adhere to tidyverse style guide.

## Question 1

How many observations and variables are there? What does each observation represent? Answer with inline code when appropriate.

```{r echo = FALSE, eval = FALSE}
glimpse(metro_bike)
```

There are `r nrow(metro_bike)` observations and `r ncol(metro_bike)` variables. A single observation represents one bike rental.

## Question 2

Make a plot that shows the number of rentals by each pass type.

```{r}
ggplot(metro_bike, aes(x = passholder_type)) +
  geom_bar()
```

## Question 3

Does bike type preference seem to vary by passholder type? Make a plot and refer to it in your answer to this question.

```{r}
ggplot(metro_bike, aes(x = passholder_type, fill = bike_type)) +
  geom_bar()
```
