---
title: "Quiz 1: Data Visualization"
author: "Sergent Gamma"
output: html_document
---

As soon as you open this document, you should knit it to make sure it knits.

```{r message=FALSE}
library(tidyverse)
library(openintro)
library(ggplot2)
options(scipen=10000)
metro_bike <- read_csv("data/metro-bike.csv")
```

The following questions will be based on the bike rental data in Los Angeles. The data represents all bike rides from Metro Bike Share company in April-June of 2019. 

The data and a description of each variable can be found at (https://bikeshare.metro.net/about/data/).

Throughout the homework, make sure you use a reasonable font size and label axes. You are welcome to use colors and themes whenever you would like. Adhere to tidyverse style guide.

## Question 1

How many observations and variables are there? What does each observation represent? Answer with inline code when appropriate.

```{r}
glimpse(metro_bike)
```

There are 64,555 observations and 15 variables. One variable represents a person's bike rental trip.

## Question 2

Make a plot that shows the number of rentals by each pass type.

```{r}
metro_bike %>% 
  ggplot() +
  aes(x = passholder_type, fill = passholder_type) +
  geom_bar() +
  xlab("Passholder Type") +
  ylab("Count") +
  ggtitle("Metro Bike Share Passholder Type for April - June of 2019") +
  guides(fill = guide_legend(title = "Passholder type")) +
  theme_bw()
```


## Question 3

Does bike type preference seem to vary by passholder type? Make a plot and refer to it in your answer to this question.


```{r}
metro_bike %>% 
  ggplot() +
  aes(x = passholder_type, fill = bike_type) +
  geom_bar(position="fill") +
  xlab("Passholder Type") +
  ylab("Percent of rentals") +
  ggtitle("Metro Bike Share Passholder Type by Bike Type for April - June of 2019") +
  guides(fill = guide_legend(title = "Bike Type")) +
  theme_bw()
```

Yes, bike type preference does seem to vary by passholder type. Overall, standard bike are preferred, aside from testing. One day passholders and walk-ups rent more smart than electric bikes, whereas the opposite is true for annual and monthly pass holders.
